Thermodynamic fragments for magic states in quantum computation

### 2021-03-25 magic_paper.tex
added citations

\begin{document}
% - vs -- (n-copy, sigma-fragment etc.)
% Plot consistency (esp Figs. 3, 4, 5, 6)
%
%
%

@@

\begin{enumerate}
    \item Fault-tolerance~\cite{cit:raussendorf, cit:gross2, cit:markov, cit:gross, cit:nest, cit:nest2, cit:vidal, cit:fujii, cit:gottesman}
    \item Magic~\cite{cit:veitch, cit:veitch2, Wang_2019, Wang_2018, cit:howard, cit:campbell, cit:gross3, cit:gross4}
    \item Bringing in majorisation~\cite{cit:cwiklinski, cit:lostaglio2, cit:lostaglio, cit:gour, cit:janzing, cit:brandao2, cit:gour2, cit:marshall, cit:nielsen}
\end{enumerate}

@@

Magic states are necessary for achieving universal quantum computation within fault-tolerant schemes.
Identifying magic as a resource for quantum universality has led to several theories which try to provide a framework for its quantification and manipulation \nick{CITE}.
The main question that such a theory attempts to answer is:
\begin{center}
    \emph{Given two magic states $\rho$ and $\rho'$ is there a free operation that can convert $\rho$ to $\rho'$?}
\end{center}

We are interested in all resource theories of magic $\R = (\F, \O)$ in which free operations cannot generate any amount of resource. 
Further denote by $\D$ the set of states considered under the theory, that is the union of free and resource states.
The structure of such theory is described by a partial order \nick{CITE}, hereinafter called a \emph{pre-order}, $\prec_{\R}$ between states.
We write $\rho' \prec_{\R} \rho$ iff there exists $\E \in \O$ such that $\E(\rho) = \rho'$.
Naturally, states may be incomparable under the given theory, meaning that there exists no free operation that converts one to the other.
We further call $\R' = (\F', \O')$ a \emph{subtheory} of $\R$ iff $\F' \subseteq \F$ and $\O' \subseteq \O$. 
The above notation will be used for general resource theories as well.

Formally, the no resource generation condition on the theories translates into two assumptions:
\begin{enumerate}[I]
    \item Free operations send free states into free states, $\E: \F \mapsto \F$, for all $\E \in \O$;
    \item Resource theory $\R$ is a completely free state preserving theory, in the sense that for any $d$-dimensional ancilla system and all free operations $\E$, $(\id_d \otimes \E ) \sigma \in \F$ whenever $\sigma \in \F$.
\end{enumerate}
The first assumption simply states that resources cannot be generated for free and is a minimal requirement for a resource theory. 
An immediate consequence is that if statistical mixing is included in $\O$, then the resource theory is convex.
Convex resource theories have attracted a lot of attention recently \nick{CITE} and include the magic theories discussed in~\cref{sec:prev}.
The second assumption implies that resources cannot be generated even when ancillas are allowed \nick{example of T state generation on Bell state by Campbell}.

Monotones are often used \nick{CITE} to address the question of state convertibility, although such approaches are usually generic.

The monotonicity condition reflects the no resource generating property of free operations, so that monotones respect the pre-order $\prec_\R$ of the theory.
A monotone of any general resource theory is a projection of the theory onto the non-negative real numbers, collapsing the pre-order of the theory to the total order defined on the real line.
Our contribution is the introduction of a generalised notion of \emph{resource projection} which maps a general resource theory onto a subtheory which in principle still retains a partial structure (as opposed to the real line).
Applying this notion on existing magic theories highlights the hidden stochasticity that governs magic state conversions.
We show that a magic theory can be subdivided into \emph{fragments} \nick{expand}

@@

\ddd{[Section needs a lot of fixing]}

The stabiliser theory of magic comprises of the so-called ``stabiliser'' states ($\stab$) and operations ($\so$), while non-stabiliser (resource) states are called magic.
The stabiliser operations can be expressed in terms of a Stinespring dilation as 
\begin{equation}
    \E(\rho) = \tr_E [U(\rho \otimes \sigma_E)U^\dagger],
\end{equation} 
for an ancilla stabiliser state $\sigma_E$. 
The motivation of the theory stems from the fact that stabiliser operations are experimentally straightforward to implement and they can be used to detect and correct errors on the stabiliser states due to their construction \nick{CITE}.
The Gottesman-Knill theorem however indicates that stabiliser operations need to be supplemented with magic states in order to achieve universality, justifying the term ``magic''.

Generalisations of the stabiliser theory appear in the literature intending to include broader classes of operations \nick{CITE}.
The class of stabiliser preserving operations ($\spo$) is defined as the set of $\cptp$ maps that send stabiliser states into stabiliser states~\cite{cit:ahmadi}.
An important subclass of $\spo$ is the set of completely stabiliser preserving operations ($\cspo$), which intuitively cannot induce ``non-stabiliserness'' even when applied to only part of a quantum state, i.e. operations $\E$ such that $(\id_d \otimes \E ) \sigma \in \stab$ for all positive dimensions $d$ whenever $\sigma \in \stab$.

Even though non-stabiliserness is a necessary resource for universality, it has been proven insufficient for magic state distillation~\cite{cit:bravyi, cit:campbell}.
In fact, all states with non-negative Wigner distributions have been proven to be efficiently classically simulable in~\cite{cit:mari}, a result that serves as a generalization of the Gottesman-Knill theorem.
The Wigner distribution of a state in odd prime dimensions is discussed rigorously in~\cref{sec:wigner} and arises as the unique quasi-probability representation of quantum theory that identifies non-contextuality exactly with the states that are efficiently classically simulable~\cite{cit:howard2, cit:veitch2}.
In this framework, the stabiliser states are the only pure states represented with non-negative distributions~\cite{cit:gross3}. 
However, there exist mixed states with non-negative Wigner distributions that are not mixtures of stabiliser states~\cite{cit:gross}.
Therefore, stabiliser-preserving theories have been extended to a theory that preserves state ``Wigner positivity''~\cite{Wang_2019}, formally defined in~\cref{sec:wigner} for odd prime dimensions.
Informally, it can be considered as the maximal theory of magic $\Rmax = (\Fmax, \Omax)$, where free states have non-negative Wigner distributions and free operations completely preserve this property.\\

@@

The displacement operators form the Heisenberg-Weyl group \nick{CITE} under matrix multiplication modulo phases,
\begin{equation}\label{eq:gp}
    {\rm{HW}}_d^n \coloneqq \{ \tau^k D_{\bmx}: k \in \mathbb{Z}_d, \bmx \in \cal{P}_d^n\}.
\end{equation}
The Clifford operations $ \cal{C}_d^n $ are then defined as the set of unitaries that normalise the Heisenberg-Weyl group. We may define the pure stabiliser states as those states obtained by acting on $|0\>$ with Clifford unitaries. Finally, we define $\stab$ as the convex hull of all pure stabiliser states, namely all probabilistic mixtures of states of the form $U|0\>\<0|U^\dagger$ where $U$ is some Clifford unitary. The stabiliser theory forms a magic resource theory $\R = (\stab, \so)$
and the free operations are stabiliser operations ($\so$), defined as compositions of preparation of computational basis states, Clifford unitaries, measurement in the computational basis, and the ability to discard subsystems.

@@

For any quantum state $\rho$, the Wigner distribution $W_\rho(\bmx)$ is readily seen to be a $d^2$-dimensional quasi-probability distribution over $\cal{P}_d$ (see~\cref{app:wigner} for details).  In~\cref{fig:wstate_examples}, we show Wigner distributions of different types of qutrit states.
\begin{figure}%
    \centering
    \subfigure[][]{%
    \label{fig:maxmix}%
    \includegraphics[height=2cm]{figs/maxmixed.pdf}
    %\caption{Maximally mixed state $\frac{1}{3}\id$}%
    }\hspace{8pt}%
    \subfigure[][]{%
    \label{fig:zero}%
    \includegraphics[height=2cm]{figs/zerostate.pdf}
    %\caption{Zero state $\ketbra{0}{0}$}%
    }\\
    \subfigure[][]{%
    \label{fig:bound}%
    \includegraphics[height=2cm]{figs/boundstate.pdf}
    %\caption{Bound state}%
    }\hspace{8pt}%
    \subfigure[][]{%
    \label{fig:strange}%
    \includegraphics[height=2cm]{figs/strangestate.pdf}
    %\caption{Strange state $\ketbra{S}{S}$}%
    }
    \caption{\textbf{Qutrit Wigner distributions of varying magic.} 
    \subref{fig:maxmix} Maximally mixed state $\frac{1}{3}\id$; \subref{fig:zero} Stabilizer zero state $\ketbra{0}{0}$; \subref{fig:bound} A non-stabiliser Wigner-positive state; \subref{fig:strange} Magic Strange state $\ket{{\rm{S}}} = \frac{1}{\sqrt{2}}(\ket{1} - \ket{2})$, coined in~\cite{cit:veitch2}.
    }%
    \label{fig:wstate_examples}
\end{figure}

@@

One of the most fundamental and commonly used magic monotones is the \emph{mana} of a state~\cite{cit:veitch2}, defined as
\begin{equation}
    \mana{\rho} \coloneqq \ln{(2\hspace{1pt}\sn{\rho}+1)},
\end{equation}
where the \emph{sum-negativity}~\cite{cit:veitch2} is the sum of the negative components in $\W{\rho}$,
\begin{equation}
    \sn{\rho} \coloneqq \sum\limits_{\bmx: \W[\bmx]{\rho} < 0} \abs{\W[\bmx]{\rho}}.
\end{equation}
Mana is an additive\footnote{It satisfies the condition $\mana{\rho_1 \otimes \rho_2} = \mana{\rho_1} + \mana{\rho_2}$ which is practical in distillation settings.} magic monotone, so it provides an analytical, necessary condition for many-copy magic state interconvertibility.
The magic monotone of \emph{max--thauma}~\cref{Wang_2018} has also been introduced more recently for qudits of odd prime dimension.

@@

Majorisation is a collection of powerful tools that has recently found many applications in quantum information theory \nick{CITE}.
It describes the \nick{disorder / non-uniformity} of distributions that undergo stochastic transformations.

@@

Majorisation describes quantum thermodynamics exactly in the absence of quantum coherence.
The use of majorisation in this setting provides vital intuition for our purposes.
At any given temperature $\beta^{-1}$, the thermal state $\gamma_\beta$ is thermodynamically the most disordered state. 
Thermal operations are defined as operations that cannot extract energy from the Gibbs state, $\E(\gamma_\beta) = \gamma_\beta$.
Convertibility between states via thermal operations is equivalent to a stochasticity condition on the energy level populations of the states \nick{CITE}.
Informally, there exists a thermal operation $\E$ such that $\tau = \E(\rho)$ if and only if there exists a matrix $S \in \stoch$ such that $\bm{q} = S\bm{p}$, where $\bm{q}, \bm{p}$ and $\bmd$ and the energy level population vectors of $\tau, \rho, \gamma_\beta$ respectively.

Based on this setting, we define $\bmd$--majorisation as follows.
\begin{definition}[\textbf{$\boldsymbol\bmd$--majorisation}]\label{def:dmajor}
    Given $\bmx, \bmy, \bmd \in \reals^d$, such that the components of $\bmd$ are positive, $\bmy$ is said to $\bmd$--majorise $\bmx$, iff there exists a $\bmd$--stochastic matrix $S$ such that $\bmx = S\bmy$.
\end{definition}
We denote this pre-order by $\bmx \prec_{\bmd} \bmy$.
If $\bmd = \frac{1}{d}\bm{1}$, the $d$-dimensional uniform distribution, then $\stoch$ is the set of doubly stochastic matrices and we retrieve the familiar notion of majorisation from entanglement theory. \nick{CITE}

@@

Given this context we now define the following key notion, that is central to our analysis.
\begin{definition}[\textbf{$\boldsymbol\sigma$-fragment}]\label{def:sigmafrag}
   Given a resource theory of magic $\R = (\F, \O)$, the \emph{$\sigma$--fragment of $\R$} is the resource theory $\R_\sigma = (\F_\sigma, \O_\sigma)$, where $\F_\sigma = \{\sigma\}$ and the free operations are restricted to the ones that leave $\sigma$ invariant,
    \begin{equation}
        \O_\sigma \coloneqq \{ \E \in \O: \E(\sigma) = \sigma \}.
    \end{equation}
\end{definition}

@@

    Conversely, suppose $\E$ is in $\O$. 
    The free states are a closed set that is mapped one-to-one to a closed subset $\cal{S}$ of the $(d^2 - 1)$-dimensional probability simplex.
    $\cal{S}$ is convex, since any combination of free states is also free and the Wigner distribution is linear.
    Therefore, $\cal{S}$ is convex and compact as a closed convex subset of the bounded compact probability simplex.

    We can now view $\W{\E}$ as a stochastic, continuous mapping from $\cal{S}$ to itself, thus Brouwer's fixed point theorem \nick{CITE} implies that there exists a probability distribution $d_{\bmz}$ for some $ \bmz \in \cal{P}_d$ that is a fixed point of $\W{\E}$.
    This corresponds to a free state $\sigma \coloneqq \sum_{\bmz \in \cal{P}_d} d_{\bmz} A_{\bmz} \in \F$. 
    Therefore $\E \in \O_\sigma$, and so $\O = \bigcup\limits_{\sigma \in \F} \O_\sigma$.

    The state interconversion result follows immediately.
\end{proof}
\begin{figure}[t]
    \centering
        \includegraphics[scale=0.3
        ]{figs/operations.pdf}
    \caption{\textbf{Decomposition of a magic theory $\R$ intro $\sigma$--fragments.} 
	Examples of magic theories ($\so$: Stabilizer operations, $\Omax$: Completely positive-Wigner-preserving operations, $\rcu$: Random Clifford Unitaries -- subclass of $\so$) involve operations denoted by the two yellow regions, with every other established magic theory  between them.
    We introduce $\sigma$--fragments $\O_\sigma$ defined for all free states $\sigma$ that cover $\Omax$. 
    Each $\O_\sigma$ is extensible to a set of stochastic maps outside the $\cptp$ operations.
    Within each $\sigma$--fragment $\bmd$--majorisation can be used allowing for tractable approach towards the study of magic state interconversion.
    }
    \label{fig:zoo}
\end{figure}

@@

It is then apparent that the pre-order $\prec_{\R_\sigma}$ between the operations in the $\sigma$--fragment follows the rules of $\bmd$--majorisation as outlined in~\cref{sec:major}.
In particular, the pre-order $\prec_{\R_\sigma}$ of the $\sigma$--fragment $\R_\sigma = (\F, \O_\sigma)$ between $d$-dimensional states corresponds to the majorisation pre-order $\prec_{\W{\sigma}}$ between their $d^2$-dimensional Wigner distributions.
For simplicity we shall merge the notation into $\prec_\sigma$, as there is little risk of confusion.

Note that the Wigner components of an $n$-copy state $\rho^{\otimes n}$ can be calculated directly from $\W{\rho}$ by convolution of the distribution with itself,
\begin{equation}
	\W{\rho^{\otimes n}} = \W{\rho}^{\otimes n},
\end{equation}
where $\otimes$ can be interpreted as the usual Kronecker product in the last expression.
We may use the vector notation $\bmw(\rho) = (w(\rho)_i)_{i=1,\dots,d^2}$ for the Wigner distribution, in which case we can express the Kronecker product as
\begin{equation}
	\W{\rho} \otimes \W{\rho} = (w(\rho)_i w(\rho)_j)_{i,j=1,\dots,d^2}.
\end{equation}
The correspondence between the phase space and pure vector representations of the Wigner distribuition is discussed more in~\cref{app:cmpairs}.
\nick{In the rest of the paper we will be using the two notations interchangeably.}

Furthermore, we restrict our analysis to $\sigma$--fragments, where $\sigma$ is full-rank.
This is justified as majorisation is continuous between fragments, in the sense that the pre-orders $\prec_\sigma$ and $\prec_{\sigma'}$ are equivalent for states $\sigma$ and $\sigma'$ which are $\epsilon$-close. \nick{CHECK}
Therefore, majorisation analysis is robust under imperfections in the experimental implementation of quantum operations.

@@

This approach can also provide \emph{lower bounds} on distillation, however now more structure about the specific free operations must be included. 
We briefly discuss distillation lower bounds in~\nick{REF}.

@@

In~\cref{sec:unital,sec:stab}, we study majorisation constraints on magic distillation arising in different fragments. 
For this reason, we define the $n$-copy, $\epsilon$-noisy Strange state,
\begin{equation}\label{eq:noisysn}
    \rho_{\rm{S}}(\epsilon)^{\otimes n} \coloneqq \left[ (1 - \epsilon) \ket{\rm{S}}\bra{\rm{S}} + \epsilon \frac{1}{3}\id \right]^{\otimes n},
\end{equation}
in $\O_\sigma$, where the pure magic state $\ket{\rm{S}}$ is induced with depolarising noise. 
Its Wigner distribution is visualised in~\cref{fig:strange}.

@@

In~\cref{fig:lcs}, we illustrate the Lorenz curve $\lc{\rho_{\rm{S}}}{\sigma}$\footnote{Hereinafter, we may drop parameters $\epsilon$ and $n$ for clarity} of pure and noisy $n$-copy Strange states in some thermal $\sigma$--fragment.
Due to~\cref{lem:lcmax}, it is clear that the curves peak at $1 + \sn{\rho_{\rm{S}}(\epsilon)^{\otimes n}}$.
\begin{figure}
    \centering
    \includegraphics[height=5cm]{figs/lc_strange.pdf}
    \caption{\textbf{Strange state Lorenz curves.} Lorenz curves of $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ for $n=1,2,3,4$ in the $\sigma$--fragment where $\sigma = e^{-\beta H}/\Z_{\beta}$, with Hamiltonian spectrum $(0,1,2)$ over the computational basis and $\beta = 0.5$.
    Solid lines represent pure Strange states ($\epsilon = 0$); dashed lines represent noisy Strange states ($\epsilon = 0.1$).
    }
    \label{fig:lcs}
\end{figure}

@@

The component values and multiplicities ($m_i$) in the $n$-copy case are 
\begin{align}
	m_i &= 8^{2i}\binom{n}{2i}, \\
	w(\rho_{\rm{S}})_i &= u^{2i}(-v)^{n-2i}, \\
	w(\id/3)_i &=  \frac{1}{9^n},
\end{align}
where index $i$ runs through $0,\dots,\frac{n}{2}$.
This is derived in~\cref{app:lcsu_coord_elb}.

>>>>

\begin{document}
% - vs -- (n-copy, sigma--fragment etc.)
% Distillation rate vs bound
% Sec: Appendix D
% Sec: Intro
% Sec: General resources
% Sec: Lower bounds
% Sec: Abstract
% Plot consistency (esp. figs 3,4,5,6)
% Spacing

@@

@@

Magic states are necessary for achieving universal quantum computation within fault-tolerant schemes~\cite{cit:veitch, cit:mari, cit:gottesman, cit:bravyi, cit:knill, Campbell_2011}.
Identifying magic as a resource for quantum universality has led to several theories which try to provide a framework for its quantification and manipulation \cite{cit:veitch2, cit:howard, Wang_2019, Seddon_2021}.
The main question that such a theory attempts to answer is:
\begin{center}
    \emph{Given two magic states $\rho$ and $\rho'$ is there a free operation that can convert $\rho$ to $\rho'$?}
\end{center}

We are interested in all resource theories of magic $\R = (\F, \O)$ in which free operations cannot generate any amount of resource. 
Further denote by $\D$ the set of states considered under the theory, that is the union of free and resource states.
The structure of such theory is described by a partial order, hereinafter called a \emph{pre-order}, $\prec_{\R}$ between states.
We write $\rho' \prec_{\R} \rho$ iff there exists $\E \in \O$ such that $\E(\rho) = \rho'$.
Naturally, states may be incomparable under the given theory, meaning that there exists no free operation that converts one to the other.
We further call $\R' = (\F', \O')$ a \emph{subtheory} of $\R$ iff $\F' \subseteq \F$ and $\O' \subseteq \O$. 
The above notation will be used for general resource theories as well.

Formally, the no resource generation condition on the theories translates into two assumptions:
\begin{enumerate}[I]
    \item Free operations send free states into free states, $\E: \F \mapsto \F$, for all $\E \in \O$;
    \item Resource theory $\R$ is a completely free state preserving theory, in the sense that for any $d$--dimensional ancilla system and all free operations $\E$, $(\id_d \otimes \E ) \sigma \in \F$ whenever $\sigma \in \F$.
\end{enumerate}
The first assumption simply states that resources cannot be generated for free and is a minimal requirement for a resource theory. 
An immediate consequence is that if statistical mixing is included in $\O$, then the resource theory is convex.

Monotones are often used to address the question of state convertibility, although such approaches are usually generic.

The monotonicity condition reflects the no resource generating property of free operations, so that monotones respect the pre-order $\prec_\R$ of the theory.
A monotone of any general resource theory is a projection of the theory onto the non-negative real numbers, collapsing the pre-order of the theory to the total order defined on the real line.
Our contribution is the introduction of a generalised notion of \emph{resource projection} which maps a general resource theory onto a subtheory which in principle still retains a partial structure (as opposed to the real line).
Applying this notion on existing magic theories highlights the hidden stochasticity that governs magic state conversions.
We show that a magic theory can be subdivided into \emph{fragments} \nick{FIX AND EXPAND}

@@

The stabiliser theory of magic comprises of the so-called ``stabiliser'' states ($\stab$) and operations ($\so$), while non-stabiliser (resource) states are called magic.
The stabiliser operations can be expressed in terms of a Stinespring dilation as 
\begin{equation}
    \E(\rho) = \tr_E [U(\rho \otimes \sigma_E)U^\dagger],
\end{equation} 
for an ancilla stabiliser state $\sigma_E$. 
The motivation of the theory stems from the fact that stabiliser operations are experimentally straightforward to implement and they can be used to detect and correct errors on the stabiliser states due to their construction \cite{cit:gottesman, cit:gottesman2, cit:gottesman1998}.
The Gottesman-Knill theorem however indicates that stabiliser operations need to be supplemented with magic states in order to achieve universality, justifying the term ``magic''.

Generalisations of the stabiliser theory appear in the literature intending to include broader classes of operations.
The class of stabiliser preserving operations ($\spo$) is defined as the set of $\cptp$ maps that send stabiliser states into stabiliser states~\cite{cit:ahmadi}.
An important subclass of $\spo$ is the set of completely stabiliser preserving operations ($\cspo$)~\cite{cit:seddon}, which intuitively cannot induce ``non-stabiliserness'' even when applied to only part of a quantum state, i.e. operations $\E$ such that $(\id_d \otimes \E ) \sigma \in \stab$ for all positive dimensions $d$ whenever $\sigma \in \stab$.

Even though non-stabiliserness is a necessary resource for universality, it has been proven insufficient for magic state distillation~\cite{cit:bravyi, cit:campbell}.
In fact, all states with non-negative Wigner distributions have been proven to be efficiently classically simulable in~\cite{cit:mari}, a result that serves as a generalization of the Gottesman-Knill theorem.
The Wigner distribution of a state in odd prime dimensions, formally defined in~\cref{sec:wigner}, arises as the unique quasi-probability representation of quantum theory that identifies non-contextuality exactly with the states that are efficiently classically simulable~\cite{Delfosse_2017, cit:howard2, cit:veitch2}.
In this framework, the stabiliser states are the only pure states represented with non-negative distributions~\cite{cit:gross3}. 
However, there exist mixed states with non-negative Wigner distributions that are not mixtures of stabiliser states~\cite{cit:gross}.
Therefore, stabiliser-preserving theories have been extended to a theory that preserves state ``Wigner positivity''~\cite{Wang_2019}.
Informally, it can be considered as the maximal theory of magic $\Rmax = (\Fmax, \Omax)$, where free states have non-negative Wigner distributions and free operations completely preserve this property.\\

@@

The displacement operators form the Heisenberg-Weyl group~\cite{Folland_1989, Bengtsson_2006} under matrix multiplication modulo phases,
\begin{equation}\label{eq:gp}
    {\rm{HW}}_d^n \coloneqq \{ \tau^k D_{\bmx}: k \in \mathbb{Z}_d, \bmx \in \cal{P}_d^n\}.
\end{equation}
The Clifford operations $ \cal{C}_d^n $ are then defined as the set of unitaries that normalise the Heisenberg-Weyl group. We may define the pure stabiliser states as those states obtained by acting on $|0\>$ with Clifford unitaries. Finally, we define $\stab$ as the convex hull of all pure stabiliser states, namely all probabilistic mixtures of states of the form $U|0\>\<0|U^\dagger$ where $U$ is some Clifford unitary. The stabiliser theory forms a magic resource theory $\R = (\stab, \so)$
and the free operations are stabiliser operations ($\so$), defined as compositions of preparation of computational basis states, Clifford unitaries, measurement in the computational basis, and the ability to discard subsystems.

@@

For any quantum state $\rho$, the Wigner distribution $W_\rho(\bmx)$ is readily seen to be a $d^2$--dimensional quasi-probability distribution over $\cal{P}_d$ (see~\cref{app:wigner} for details).  In~\cref{fig:wstate_examples}, we show Wigner distributions of different types of qutrit states.
\begin{figure}%
    \centering
    \subfigure[][]{%
    \label{fig:maxmix}%
    \includegraphics[height=2cm]{figs/maxmixed.pdf}
    %\caption{Maximally mixed state $\frac{1}{3}\id$}%
    }\hspace{8pt}%
    \subfigure[][]{%
    \label{fig:zero}%
    \includegraphics[height=2cm]{figs/zerostate.pdf}
    %\caption{Zero state $\ketbra{0}{0}$}%
    }\\
    \subfigure[][]{%
    \label{fig:bound}%
    \includegraphics[height=2cm]{figs/boundstate.pdf}
    %\caption{Bound state}%
    }\hspace{8pt}%
    \subfigure[][]{%
    \label{fig:strange}%
    \includegraphics[height=2cm]{figs/strangestate.pdf}
    %\caption{Strange state $\ketbra{S}{S}$}%
    }
    \caption{\textbf{Qutrit Wigner distributions of varying magic.} 
    \subref{fig:maxmix} Maximally mixed state $\frac{1}{3}\id$; \subref{fig:zero} Stabilizer zero state $\ketbra{0}{0}$; \subref{fig:bound} A non-stabiliser Wigner-positive state; \subref{fig:strange} Magic Strange state $\ket{{\rm{S}}} = \frac{1}{\sqrt{2}}(\ket{1} - \ket{2})$, coined in~\cite{cit:veitch2}.
    }%
    \label{fig:wstate_examples}
\end{figure}

@@

One of the most fundamental and commonly used magic monotones is the \emph{mana} of a state~\cite{cit:veitch2}, defined as
\begin{equation}
    \mana{\rho} \coloneqq \ln{(2\hspace{1pt}\sn{\rho}+1)},
\end{equation}
where the \emph{sum-negativity}~\cite{cit:veitch2} is the sum of the negative components in $\W{\rho}$,
\begin{equation}
    \sn{\rho} \coloneqq \sum\limits_{\bmx: \W[\bmx]{\rho} < 0} \abs{\W[\bmx]{\rho}}.
\end{equation}
Mana is an additive\footnote{It satisfies the condition $\mana{\rho_1 \otimes \rho_2} = \mana{\rho_1} + \mana{\rho_2}$ which is practical in distillation settings.} magic monotone, so it provides an analytical, necessary condition for many-copy magic state interconvertibility.
The magic monotone of \emph{max--thauma}~\cite{Wang_2018} has also been introduced more recently for qudits of odd prime dimension.

@@

Majorisation~\cite{cit:marshall} is a collection of powerful tools that has recently found many applications in quantum information theory~\cite{Nielsen_1999, cit:cwiklinski, cit:lostaglio2, cit:gour, cit:gour2, Horodecki_2003, Vallejos_2021}.
It describes the \nick{disorder / non-uniformity} of distributions that undergo stochastic transformations.

@@

Majorisation describes quantum thermodynamics exactly in the absence of quantum coherence.
The use of majorisation in this setting provides vital intuition for our purposes.
At any given temperature $\beta^{-1}$, the thermal state $\gamma_\beta$ is thermodynamically the most disordered state. 
Thermal operations are defined as operations that cannot extract energy from the Gibbs state, $\E(\gamma_\beta) = \gamma_\beta$.
Convertibility between states via thermal operations is equivalent to a stochasticity condition on the energy level populations of the states~\cite{cit:lostaglio}.
Informally, there exists a thermal operation $\E$ such that $\tau = \E(\rho)$ if and only if there exists a matrix $S \in \stoch$ such that $\bm{q} = S\bm{p}$, where $\bm{q}, \bm{p}$ and $\bmd$ and the energy level population vectors of $\tau, \rho, \gamma_\beta$ respectively.

Based on this setting, we define $\bmd$--majorisation as follows.
\begin{definition}[\textbf{$\boldsymbol\bmd$--majorisation}]\label{def:dmajor}
    Given $\bmx, \bmy, \bmd \in \reals^d$, such that the components of $\bmd$ are positive, $\bmy$ is said to $\bmd$--majorise $\bmx$, iff there exists a $\bmd$--stochastic matrix $S$ such that $\bmx = S\bmy$.
\end{definition}
We denote this pre-order by $\bmx \prec_{\bmd} \bmy$.
If $\bmd = \frac{1}{d}\bm{1}$, the $d$--dimensional uniform distribution, then $\stoch$ is the set of doubly stochastic matrices and we retrieve the familiar notion of majorisation from entanglement theory~\cite{Nielsen_1999}.

@@

Given this context we now define the following key notion, that is central to our analysis.
\begin{definition}[\textbf{$\boldsymbol\sigma$--fragment}]\label{def:sigmafrag}
   Given a resource theory of magic $\R = (\F, \O)$, the \emph{$\sigma$--fragment of $\R$} is the resource theory $\R_\sigma = (\F_\sigma, \O_\sigma)$, where $\F_\sigma = \{\sigma\}$ and the free operations are restricted to the ones that leave $\sigma$ invariant,
    \begin{equation}
        \O_\sigma \coloneqq \{ \E \in \O: \E(\sigma) = \sigma \}.
    \end{equation}
\end{definition}

@@

    Conversely, suppose $\E$ is in $\O$. 
    The free states are a closed set that is mapped one-to-one to a closed subset $\cal{S}$ of the $(d^2 - 1)$--dimensional probability simplex.
    $\cal{S}$ is convex, since any combination of free states is also free and the Wigner distribution is linear.
    Therefore, $\cal{S}$ is convex and compact as a closed convex subset of the bounded compact probability simplex.

    We can now view $\W{\E}$ as a stochastic, continuous mapping from $\cal{S}$ to itself, thus Brouwer's fixed point theorem~\cite{cit:brouwer} implies that there exists a probability distribution $d_{\bmz}$ for some $ \bmz \in \cal{P}_d$ that is a fixed point of $\W{\E}$.
    This corresponds to a free state $\sigma \coloneqq \sum_{\bmz \in \cal{P}_d} d_{\bmz} A_{\bmz} \in \F$. 
    Therefore $\E \in \O_\sigma$, and so $\O = \bigcup\limits_{\sigma \in \F} \O_\sigma$.

    The state interconversion result follows immediately.
\end{proof}
\begin{figure}[t]
    \centering
        \includegraphics[scale=0.3
        ]{figs/operations.pdf}
    \caption{\textbf{Decomposition of a magic theory $\R$ intro $\sigma$--fragments.} 
	Examples of magic theories ($\so$: Stabilizer operations, $\Omax$: Completely positive-Wigner-preserving operations, $\rcu$: Random Clifford Unitaries -- subclass of $\so$) involve operations denoted by the two yellow regions, with other established magic theories  between them.
    We introduce $\sigma$--fragments $\O_\sigma$ defined for all free states $\sigma$ that cover $\Omax$. 
    Each $\O_\sigma$ is extensible to a set of stochastic maps outside the $\cptp$ operations.
    Within each $\sigma$--fragment $\bmd$--majorisation can be used allowing for tractable approach towards the study of magic state interconversion.
    }
    \label{fig:zoo}
\end{figure}

@@

It is then apparent that the pre-order $\prec_{\R_\sigma}$ between the operations in the $\sigma$--fragment follows the rules of $\bmd$--majorisation as outlined in~\cref{sec:major}.
In particular, the pre-order $\prec_{\R_\sigma}$ of the $\sigma$--fragment $\R_\sigma = (\F, \O_\sigma)$ between $d$--dimensional states corresponds to the majorisation pre-order $\prec_{\W{\sigma}}$ between their $d^2$--dimensional Wigner distributions.
For simplicity we shall merge the notation into $\prec_\sigma$, as there is little risk of confusion.

Note that the Wigner components of an $n$--copy state $\rho^{\otimes n}$ can be calculated directly from $\W{\rho}$ by convolution of the distribution with itself,
\begin{equation}
	\W{\rho^{\otimes n}} = \W{\rho}^{\otimes n},
\end{equation}
where $\otimes$ can be interpreted as the usual Kronecker product in the last expression.
We may use the vector notation $\bmw(\rho) = (w(\rho)_i)_{i=1,\dots,d^2}$ for the Wigner distribution, in which case we can express the Kronecker product as
\begin{equation}
	\W{\rho} \otimes \W{\rho} = (w(\rho)_i w(\rho)_j)_{i,j=1,\dots,d^2}.
\end{equation}
The correspondence between the phase space and pure vector representations of the Wigner distribution is discussed more in~\cref{app:cmpairs}.
The vector notation will be useful in the proof of our main result,~\cref{thm:stab_bounds}

Furthermore, we restrict our analysis to $\sigma$--fragments, where $\sigma$ is full-rank.
This is justified as majorisation is continuous between fragments, in the sense that the pre-orders $\prec_\sigma$ and $\prec_{\sigma'}$ are equivalent for states $\sigma$ and $\sigma'$ which are $\epsilon$--close. \nick{CHECK}
Therefore, majorisation analysis is robust under imperfections in the experimental implementation of quantum operations.

@@

This approach can also provide \emph{lower bounds} on distillation, however now more structure about the specific free operations must be included. 
We briefly discuss distillation lower bounds in~\cref{sec:lower_bounds}.

@@

In~\cref{sec:unital,sec:stab}, we study majorisation constraints on magic distillation arising in different fragments. 
For this reason, we define the $n$--copy, $\epsilon$--noisy Strange state,
\begin{equation}\label{eq:noisysn}
    \rho_{\rm{S}}(\epsilon)^{\otimes n} \coloneqq \left[ (1 - \epsilon) \ket{\rm{S}}\bra{\rm{S}} + \epsilon \frac{1}{3}\id \right]^{\otimes n},
\end{equation}
in $\O_\sigma$, where the pure magic state $\ket{\rm{S}}$ is induced with depolarising noise. 
Its Wigner distribution is visualised in~\cref{fig:strange}.

@@

In~\cref{fig:lcs}, we illustrate the Lorenz curve $\lc{\rho_{\rm{S}}}{\sigma}$\footnote{Hereinafter, we may omit obvious variable dependencies like $\epsilon$ and $n$ for clarity} of pure and noisy $n$--copy Strange states in some thermal $\sigma$--fragment.
Due to~\cref{lem:lcmax}, it is clear that the curves peak at $1 + \sn{\rho_{\rm{S}}(\epsilon)^{\otimes n}}$.
\begin{figure}
    \centering
    \includegraphics[height=5cm]{figs/lc_strange.pdf}
    \caption{\textbf{Strange state Lorenz curves.} Lorenz curves of $\rho_{\rm{S}}(\epsilon)^{\otimes n}$ for $n=1,2,3,4$ in the $\sigma$--fragment where $\sigma = e^{-\beta H}/\Z_{\beta}$, with Hamiltonian spectrum $(0,1,2)$ over the computational basis and $\beta = 0.5$.
    Solid lines represent pure Strange states ($\epsilon = 0$); dashed lines represent noisy Strange states ($\epsilon = 0.1$).
    }
    \label{fig:lcs}
\end{figure}

@@

The component values and multiplicities ($m_i$) in the $n$--copy case are 
\begin{align}
	m_i &= 8^{2i}\binom{n}{2i}, \\
	w(\rho_{\rm{S}})_i &= u^{2i}(-v)^{n-2i}, \\
	w(\id/3)_i &=  \frac{1}{9^n},
\end{align}
where index $i$ runs through $0,\dots,\frac{n}{2}$.
This is derived in~\cref{app:lcsu_coord_elb}.
